Are we living in a depressive society?

### 2024-04-02 outputs/paper/paper.qmd
commit

install.packages("here")

@@

# Load the dataset
data <- read.csv(file = here::here("inputs/data/Anxiety_or_Depression.csv"))

@@

# Aggregate the data by YearMonth and Indicator
aggregated_data <- filtered_data %>%
  group_by(YearMonth, Indicator) %>%
  summarise(AverageValue = mean(Value, na.rm = TRUE))

# Plot the data
ggplot(aggregated_data, aes(x = YearMonth, y = AverageValue, color = Indicator)) +
  geom_line() +
  scale_x_date(date_breaks = "6 months", date_labels = "%Y.%m") +
  labs(
    title = "National Estimates of Mental Health Symptoms",
    subtitle = "Trends of Symptoms of Anxiety and Depressive Disorders",
    x = "Year",
    y = "Rate (%)",
    color = "Indicator"
  ) +
  theme_minimal()

>>>>

# Install the following package if wasn't installed already
# install.packages("here")

@@

# Load the dataset
data <- read.csv(file = here::here("inputs/data/Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401.csv"))

@@

# Check if the YearMonth column exists
print(head(filtered_data))
print(colnames(filtered_data))

# Continue with the aggregation
aggregated_data <- filtered_data %>%
  group_by(Time.Period.End.Date, Indicator) %>%
  summarise(AverageValue = mean(Value, na.rm = TRUE))

# Plot the data
ggplot(aggregated_data, aes(x = Time.Period.End.Data, y = AverageValue, color = Indicator)) +
  geom_line() +
  scale_x_date(date_breaks = "6 months", date_labels = "%Y.%m") +
  labs(
    title = "National Estimates of Mental Health Symptoms",
    subtitle = "Trends of Symptoms of Anxiety and Depressive Disorders",
    x = "Year",
    y = "Rate (%)",
    color = "Indicator"
  ) +
  theme_minimal()
